Translation Elicitation: Report

### 2022-04-27 docs/index.Rmd
Restore workflow

Participants in the ENG-SPA listened to `r nrow(stimuli[stimuli$group=="ENG-SPA",])` Spanish words, and participants in the ENG-CAT and the SPA-CAT groups listened to `r nrow(stimuli[stimuli$group=="ENG-CAT",])` trials. Five trials in each condition were practice trials and were excluded from analyses.

@@

stimuli_coded <- stimuli %>% 
    mutate(test_language = ifelse(group=="ENG-SPA", "Spanish", "Catalan"))
```

```{r stimuli-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
    select(group, word1, frequency, frequency_zipf, pthn, lv) %>% 
    group_by(group) %>% 
    summarise_at(
        vars(frequency:lv), 
        list(
            median = ~median(., na.rm = TRUE),  
            sd = ~sd(., na.rm = TRUE)
        )
    ) %>%
    gt(rowname_col = "group") %>% 
    tab_header(
        title = md("Table 1"),
        subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
    ) %>% 
    tab_source_note(
        md("*Note*. Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
    ) %>% 
    fmt_number(frequency_median:pthn_sd) %>%
    fmt_percent(matches("lv")) %>% 
    tab_spanner(md("**Freq. (million)**"), c("frequency_median", "frequency_sd")) %>% 
    tab_spanner(md("**Freq. (Zipf)**"), matches("frequency_zipf")) %>% 
    tab_spanner(md("***PTHN***"), matches("pthn")) %>% 
    tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
    cols_label(
        frequency_median = md("Median"),
        frequency_sd = md("*SD*"),
        frequency_zipf_median = md("Median"),
        frequency_zipf_sd = md("*SD*"),
        pthn_median = md("Median"),
        pthn_sd = md("*SD*"),
        lv_median = md("Median"),
        lv_sd = md("*SD*")
    ) %>% 
    summary_rows(
        columns = c(matches("median"), -matches("lv")),
        fns = list(
            Median = "median",
            SD = "sd"
        )
    ) %>% 
    summary_rows(
        columns = matches("lv"),
        fns = list(
            Median = "median",
            SD = "sd"
        ), formatter = fmt_percent
    ) %>% 
    tab_style(
        style = cell_text(align = "left", weight = "bold", size = "medium"),
        locations = cells_title(groups = "title")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium", style = "italic"),
        locations = cells_title(groups = "subtitle")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_source_notes()
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_stub_grand_summary()
    ) %>% 
    tab_style(
        style = cell_borders(sides = c("left", "right"), color = "white"),
        locations = list(
            cells_body(), cells_row_groups(), cells_column_spanners(), 
            cells_stub(), cells_stub_grand_summary(), cells_source_notes(),
            cells_column_labels(), cells_stubhead()
        )
    ) %>% 
    tab_style(
        style = list(cell_text(align = "left", size = "medium"), cell_borders(sides = "all", color = "white")),
        locations = cells_stub()
    ) %>% 
    tab_style(
        style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
        locations = list(cells_column_spanners(), cells_column_labels())
    ) %>% 
    tab_style(
        style = cell_borders(sides = "all", color = "white"),
        locations = cells_body(columns = 1:9)
    ) %>% 
    tab_style(
        style = cell_borders(sides = "top", color = "white"),
        locations = cells_body(columns = 1:9)
    )

@@

```{r stimuli-frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
    distinct(test_language, word1, .keep_all = TRUE) %>% 
    left_join(count(., test_language, name = "n_total")) %>% 
    mutate(test_language = paste0(test_language,  " (N = ", n_total, ")")) %>% 
    ggplot(aes(frequency_zipf, fill = test_language)) +
    facet_wrap(~test_language, ncol = 1) +
    geom_histogram(bins = 25, colour = "white") +
    labs(x = "Lexical frequency (Zipf score)\nExtracted from CLEARPOND database", y = "# trials", fill = "Test language")  +
    scale_y_continuous(breaks = seq(0, 12, 2)) +
    theme(
        legend.position = "none",
        panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
    )

@@

```{r stimuli-similarity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
    left_join(count(., group, name = "n_total")) %>% 
    mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
    ggplot(aes(group, lv, fill = group, colour = group)) +
    geom_violin() +
    geom_point(shape = 1, stroke = 1, position = position_jitter(width = 0.1), colour = "black", alpha = 0.25) +
    geom_boxplot(colour = "black", fill = "white", width = 0.1, size = 0.75) +
    labs(x = "Group", y = "Phonological Leveshtein distance\n(corrected for string length)", fill = "Test language") +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
    )

@@

medians <- stimuli %>% 
    group_by(group) %>% 
    summarise(
        pthn_median = median(pthn),
        pthn_sd = sd(pthn),
        frequency_zipf_median = median(frequency_zipf),
        frequency_zipf_sd = sd(frequency_zipf),
        lv_median = median(lv),
        lv_sd = sd(lv)
    ) %>% 
    mutate(group = case_when(
        group=="ENG-CAT" ~ "cat-ENG",
        group=="ENG-SPA" ~ "spa-ENG",
        group=="SPA-CAT" ~ "cat-SPA",
    ))

# frequency
stimuli %>% 
    mutate(group = case_when(
        group=="ENG-CAT" ~ "cat-ENG",
        group=="ENG-SPA" ~ "spa-ENG",
        group=="SPA-CAT" ~ "cat-SPA",
    )) %>% 
    ggplot(aes(frequency_zipf, fill = group)) + 
    facet_wrap(~group, ncol = 1) + 
    geom_rect(
        data = medians, 
        aes(
            xmin = frequency_zipf_median-frequency_zipf_sd, xmax = frequency_zipf_median+frequency_zipf_sd, 
            ymin = -Inf, ymax = Inf, fill = group
        ), inherit.aes = FALSE, alpha = 0.15
    ) +   
    geom_histogram(bins = 20, colour = "white") +
    geom_vline(
        data = medians, 
        aes(xintercept = frequency_zipf_median, group = group), 
        colour = "black",
        size = 0.5,
        linetype = "dashed"
    ) + 
    geom_text(
        data = medians, 
        aes(
            label = "Median ± SD", 
            x = frequency_zipf_median+1.25,
            y = 13
        ), 
        size = 3
    ) +
    geom_curve(
        data = medians, 
        aes(
            x = frequency_zipf_median+0.85, 
            xend = frequency_zipf_median+0.1,
            y = 12, 
            yend = 11
        ),
        arrow = arrow(length = unit(0.2, "cm")),
        curvature = -0.25,
        colour = "grey30"
    ) +
    labs(
        x = "Lexical frequency (Zipf)", 
        y = "Number of trials", 
        title = "Frequency\n(stimuli translations)\n"
    ) +

    # PTHN
    stimuli %>% 
    count(group, pthn) %>% 
    mutate(group = case_when(
        group=="ENG-CAT" ~ "cat-ENG",
        group=="ENG-SPA" ~ "spa-ENG",
        group=="SPA-CAT" ~ "cat-SPA",
    )) %>% 
    ggplot(aes(pthn, n, fill = group)) + 
    facet_wrap(~group, ncol = 1) + 
    geom_rect(
        data = medians, 
        aes(
            xmin = 0, 
            xmax = pthn_median+pthn_sd, 
            ymin = -Inf, 
            ymax = Inf,
            fill = group
        ), inherit.aes = FALSE, 
        alpha = 0.15
    ) +   
    geom_col(colour = "white") + 
    geom_vline(
        data = medians, aes(xintercept = pthn_median, group = group), 
        colour = "black", size = 0.5, linetype = "dashed"
    ) + 
    labs(
        x = "PTHN", 
        y = "Number of trials", 
        title = "Higher-frequency neighbours\n(stimuli translations)\n"
    ) +

    # Levenshtein
    stimuli %>% 
    mutate(group = case_when(
        group=="ENG-CAT" ~ "cat-ENG",
        group=="ENG-SPA" ~ "spa-ENG",
        group=="SPA-CAT" ~ "cat-SPA",
    )) %>% 
    ggplot(aes(lv, fill = group)) +
    facet_wrap(~group, ncol = 1) + 
    geom_rect(
        data = medians, 
        aes(
            xmin = 0, xmax = lv_median+lv_sd, 
            ymin = -Inf, ymax = Inf, fill = group
        ), inherit.aes = FALSE, alpha = 0.15
    ) +   
    geom_histogram(bins = 20, colour = "white") +
    geom_vline(
        data = medians, aes(xintercept = lv_median, group = group), 
        colour = "black", size = 0.5, linetype = "dashed"
    ) + 
    scale_x_continuous(labels = percent) +
    labs(x = "Levenshtein", y = "Number of trials", title = "Phonological similarity\n(stimuli and stimuli translations)\n") +

    plot_layout(guides = "collect") &
    plot_annotation(tag_levels = "A") &
    scale_fill_manual(values = c("#1A85FF", "#ff2976", "#FFC20A"), na.translate = FALSE) &
    theme(legend.position = "none")

@@

We collected data from `r format(as_date(min(participants$date)), "%B %dth %Y")` to `r format(as_date(max(participants$date)), "%B %dth %Y")`. We tested `r length(unique(participants$participant))` participants. `r length(unique(participants$participant[participants$group=="ENG-SPA"]))` were English natives tested in Spanish, `r length(unique(participants$participant[participants$group=="ENG-CAT"]))` were English natives tested in Catalan, and `r length(unique(participants$participant[participants$group=="SPA-CAT"]))` were Spanish natives tested in Catalan. `r sum(!participants$valid_participant)` failed to meet all the inclusion criteria and were excluded from further analyses. The final sample comprised data from `r sum(!participants$valid_participant)` participants, `r sum(participants$valid_participant[participants$group=="ENG-SPA"])` in the ENG-SPA group, `r sum(participants$valid_participant[participants$group=="ENG-CAT"])` in the ENG-CAT group, and `r sum(participants$valid_participant[participants$group=="SPA-CAT"])` in the SPA-CAT group.

@@

participants_coded %>% 
    count(group, valid_participant) %>% 
    mutate(valid_participant = factor(valid_participant)) %>% 
    ggplot(aes(group, n, fill = valid_participant, order = n)) +
    geom_col() +
    labs(x = "Group", y = "# participants", fill = "Valid?") +
    theme(
        legend.title = element_blank(),
        legend.position = "top",
        axis.title.x = element_blank(),
        panel.grid.major.y = element_line(linetype = "dotted", colour = "grey")
    )

@@

participants_coded %>% 
    filter(valid_participant=="Valid") %>% 
    select(participant, group, n, n_valid) %>%
    mutate(valid_prop = n_valid/n) %>% 
    ggplot(aes(valid_prop, fill = group, colour = group)) +
    facet_wrap(~group, ncol = 1) +
    geom_histogram() +
    geom_rug() +
    labs(x = "Valid trials (%)", y = "N participants", fill = "Group", colour = "Group") +
    scale_x_continuous(limits = c(0, 1), labels = percent) +
    theme(
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank(),
        panel.grid.major.y = element_line(linetype = "dotted", colour = "grey")
    )
```

@@

```{r participants_demo, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants_valid <- filter(participants_coded, valid_participant=="Valid")

p_sex <- participants_valid %>% 
    left_join(count(participants_valid, group, name = "n_total")) %>% 
    mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
    ggplot(aes(group, fill = sex)) +
    geom_bar(position = position_fill()) +
    labs(x = "Group", y = "# participants", fill = "Sex") +
    scale_y_continuous(labels = percent) +
    theme(
        legend.position = "top",
        axis.title.x = element_blank()
    )

p_age <- participants_valid %>% 
    left_join(count(participants_valid, group, name = "n_total")) %>% 
    mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
    ggplot(aes(as.factor(age), fill = group, colour = group)) +
    facet_wrap(~group, ncol = 1) +
    geom_bar() +
    labs(x = "Age (years)", y = "% participants", fill = "Group", colour = "Group") +
    theme(
        legend.position = "none"
    )

(p_sex + p_age) &
    plot_layout() &
    plot_annotation(tag_levels = "A") &
    theme(
        legend.title = element_blank(),
        panel.grid.major.y = element_line(linetype = "dotted", colour = "grey")
    )

@@

participants_valid %>% 
    count(group, l2, .drop = FALSE) %>% 
    mutate(
        l2 = case_when(
            l2=="Alemã\u0081n" ~ "German",
            l2=="Francã\u2030s" ~ "French",
            l2=="Cuã\u0081l" ~ "Missing",
            TRUE ~ l2
        ),
    ) %>% 
    left_join(count(participants_valid, group, name = "n_total")) %>% 
    mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
    ggplot(aes(group, n, fill = l2)) +
    facet_wrap(~group, ncol = 1, scales = "free_y") +
    geom_col(position = position_fill()) +
    labs(x = "L2", y = "# participants", fill = "L2") +
    scale_y_continuous(labels = percent) +
    coord_flip() +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        strip.text = element_blank(),
        panel.grid = element_blank(),
        axis.text.x = element_text(angle = 90),
        axis.title.y = element_blank()
    )

@@

participants_valid %>% 
    select(participant, group, catalan_oral, spanish_oral, catalan_written, spanish_written) %>% 
    mutate_at(vars(catalan_oral, spanish_oral, catalan_written, spanish_written), replace_na, 0) %>% 
    pivot_longer(c(catalan_oral, spanish_oral, catalan_written, spanish_written),
                 names_to = "type", values_to = "score") %>% 
    separate(type, c("language", "modality"), sep = "_") %>% 
    mutate_at(vars(language, modality), str_to_sentence) %>%
    left_join(count(participants_valid, group, name = "n_total")) %>% 
    mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
    ggplot(aes(as.integer(score), fill = language)) +
    facet_grid(modality~group) +
    geom_bar(position = position_dodge()) +
    labs(y = "# participants", x = "Self-reported proficiency (0-5)", fill = "Language") +
    theme(
        legend.position = "top",
        panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
    )

@@

```{r responses_coded, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
responses_coded <- responses %>% 
    # typos are considered correct responses
    mutate_at(vars(group), as.factor) %>% 
    # center predictors
    mutate_at(
        vars(lv_std, pthn_std, frequency_zipf_std),
        function(x) scale(x, center = TRUE, scale = TRUE)[,1]) %>% 
    # impute missing data
    mice(m = 5, print = FALSE, method = "pmm") %>% 
    complete() %>% 
    as_tibble() %>% 
    arrange(group, word)
```

@@

coefs <- fixef(fit_6) %>% 
    as.data.frame() %>% 
    rownames_to_column("variable") %>% 
    clean_names() %>% 
    mutate_at(vars(estimate:q97_5), ~ifelse(variable=="Intercept", inv_logit_scaled(.), ./4))

str_repl <- c(
    "Intercept" = "Intercept",
    "frequency_zipf_std" = "Frequency\n[+1 SD]",
    "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
    "lv_std:groupENGvs.SPA" = "Levenshtein \u00d7 Group 1",
    "lv_std:groupENGMCATvs.ENGMSPA" = "Levenshtein \u00d7 Group 2",
    "lv_std" = "Levenshtein\n[+1 SD]",
    "pthn_std" = "PTHN\n[+1 SD]",
    "groupENGvs.SPA" =  "Group 1\n[ENG-* vs. SPA-CAT]",
    "groupENGMCATvs.ENGMSPA" = "Group 2\n[ENG-CAT vs. ENG-SPA]"
)

>>>>

Participants in the spa-ENG listened to `r nrow(stimuli[stimuli$group=="spa-ENG",])` Spanish words, and participants in the cat-ENG and the cat-SPA groups listened to `r nrow(stimuli[stimuli$group=="cat-ENG",])` trials. Five trials in each condition were practice trials and were excluded from analyses.

@@

stimuli_coded <- stimuli %>% 
  mutate(test_language = ifelse(group=="spa-ENG", "Spanish", "Catalan"))
```

```{r stimuli-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
  select(group, word1, frequency, frequency_zipf, pthn, lv) %>% 
  group_by(group) %>% 
  summarise_at(
    vars(frequency:lv), 
    list(
      median = ~median(., na.rm = TRUE),  
      sd = ~sd(., na.rm = TRUE)
    )
  ) %>%
  gt(rowname_col = "group") %>% 
  tab_header(
    title = md("Table 1"),
    subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
  ) %>% 
  tab_source_note(
    md("*Note*. Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
  ) %>% 
  fmt_number(frequency_median:pthn_sd) %>%
  fmt_percent(matches("lv")) %>% 
  tab_spanner(md("**Freq. (million)**"), c("frequency_median", "frequency_sd")) %>% 
  tab_spanner(md("**Freq. (Zipf)**"), matches("frequency_zipf")) %>% 
  tab_spanner(md("***PTHN***"), matches("pthn")) %>% 
  tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
  cols_label(
    frequency_median = md("Median"),
    frequency_sd = md("*SD*"),
    frequency_zipf_median = md("Median"),
    frequency_zipf_sd = md("*SD*"),
    pthn_median = md("Median"),
    pthn_sd = md("*SD*"),
    lv_median = md("Median"),
    lv_sd = md("*SD*")
  ) %>% 
  summary_rows(
    columns = c(matches("median"), -matches("lv")),
    fns = list(
      Median = "median",
      SD = "sd"
    )
  ) %>% 
  summary_rows(
    columns = matches("lv"),
    fns = list(
      Median = "median",
      SD = "sd"
    ), formatter = fmt_percent
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_stub_grand_summary()
  ) %>% 
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "white"),
    locations = list(
      cells_body(), cells_row_groups(), cells_column_spanners(), 
      cells_stub(), cells_stub_grand_summary(), cells_source_notes(),
      cells_column_labels(), cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(cell_text(align = "left", size = "medium"), cell_borders(sides = "all", color = "white")),
    locations = cells_stub()
  ) %>% 
  tab_style(
    style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
    locations = list(cells_column_spanners(), cells_column_labels())
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  as_raw_html()

@@

```{r stimuli-frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  distinct(
    test_language,
    word1,
    .keep_all = TRUE
  ) %>% 
  left_join(count(., test_language, name = "n_total")) %>% 
  mutate(test_language = paste0(test_language,  " (N = ", n_total, ")")) %>% 
  ggplot(
    aes(
      frequency_zipf, 
      fill = test_language
    )
  ) +
  facet_wrap(~test_language, ncol = 1) +
  geom_histogram(
    bins = 25,
    colour = "white"
  ) +
  labs(
    x = "Lexical frequency (Zipf score)\nExtracted from CLEARPOND database", 
    y = "# trials", 
    fill = "Test language"
  )  +
  scale_y_continuous(breaks = seq(0, 12, 2)) +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

@@

```{r stimuli-similarity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(count(., group, name = "n_total")) %>% 
  mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
  ggplot() +
  aes(
    x = group, 
    y = lv,
    fill = group,
    colour = group
  ) +
  geom_violin() +
  geom_point(
    shape = 1,
    stroke = 1, 
    position = position_jitter(width = 0.1), 
    colour = "black", 
    alpha = 0.25
  ) +
  geom_boxplot(
    colour = "black", 
    fill = "white",
    width = 0.1, 
    size = 0.75
  ) +
  labs(
    x = "Group", 
    y = "Phonological Leveshtein distance\n(corrected for string length)",
    fill = "Test language"
  ) +
  scale_y_continuous(
    labels = scales::percent
  ) +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(
      colour = "grey",
      linetype = "dotted"
    )
  )

@@

medians <- stimuli %>% 
  group_by(group) %>% 
  summarise(
    pthn_median = median(pthn),
    pthn_sd = sd(pthn),
    frequency_zipf_median = median(frequency_zipf),
    frequency_zipf_sd = sd(frequency_zipf),
    lv_median = median(lv),
    lv_sd = sd(lv)
  )

# frequency
stimuli %>% 
  ggplot() + 
  aes(
    x = frequency_zipf,
    fill = group
  ) + 
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = frequency_zipf_median-frequency_zipf_sd,
      xmax = frequency_zipf_median+frequency_zipf_sd, 
      ymin = -Inf,
      ymax = Inf, 
      fill = group
    ),
    inherit.aes = FALSE,
    alpha = 0.15
  ) +   
  geom_histogram(
    bins = 20,
    colour = "white"
  ) +
  geom_vline(
    data = medians, 
    aes(
      xintercept = frequency_zipf_median,
      group = group
    ), 
    colour = "black",
    size = 0.5,
    linetype = "dashed"
  ) + 
  geom_text(
    data = medians, 
    aes(
      label = "Median ± SD", 
      x = frequency_zipf_median+1.25,
      y = 13
    ), 
    size = 3
  ) +
  geom_curve(
    data = medians, 
    aes(
      x = frequency_zipf_median+0.85, 
      xend = frequency_zipf_median+0.1,
      y = 12, 
      yend = 11
    ),
    arrow = arrow(length = unit(0.2, "cm")),
    curvature = -0.25,
    colour = "grey30"
  ) +
  labs(
    x = "Lexical frequency (Zipf)", 
    y = "Number of trials", 
    title = "Frequency\n(stimuli translations)\n"
  ) +

  # PTHN
  stimuli %>% 
  count(group, pthn) %>% 
  ggplot(
    aes(
      x = pthn, 
      y = n,
      fill = group
    )
  ) + 
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = 0, 
      xmax = pthn_median+pthn_sd, 
      ymin = -Inf, 
      ymax = Inf,
      fill = group
    ), 
    inherit.aes = FALSE, 
    alpha = 0.15
  ) +   
  geom_col(colour = "white") + 
  geom_vline(
    data = medians, 
    aes(
      xintercept = pthn_median,
      group = group
    ), 
    colour = "black", 
    size = 0.5,
    linetype = "dashed"
  ) + 
  labs(
    x = "PTHN", 
    y = "Number of trials", 
    title = "Higher-frequency neighbours\n(stimuli translations)\n"
  ) +

  # Levenshtein
  stimuli %>% 
  ggplot() +
  aes(lv, fill = group) +
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = 0,
      xmax = lv_median+lv_sd, 
      ymin = -Inf,
      ymax = Inf, fill = group
    ),
    inherit.aes = FALSE,
    alpha = 0.15
  ) +   
  geom_histogram(
    bins = 20,
    colour = "white"
  ) +
  geom_vline(
    data = medians,
    aes(
      xintercept = lv_median, 
      group = group
    ), 
    colour = "black",
    size = 0.5,
    linetype = "dashed"
  ) + 
  scale_x_continuous(labels = percent) +
  labs(
    x = "Levenshtein",
    y = "Number of trials",
    title = "Phonological similarity\n(stimuli and stimuli translations)\n"
  ) +

  plot_layout(guides = "collect") &
  plot_annotation(tag_levels = "A") &
  scale_fill_manual(
    values = c("#1A85FF", "#ff2976", "#FFC20A"), 
    na.translate = FALSE
  ) &
  theme(legend.position = "none")

@@

We collected data from `r format(as_date(min(participants$date)), "%B %dth %Y")` to `r format(as_date(max(participants$date)), "%B %dth %Y")`. We tested `r length(unique(participants$participant_id))` participants. `r length(unique(participants$participant_id[participants$group=="spa-ENG"]))` were English natives tested in Spanish, `r length(unique(participants$participant_id[participants$group=="cat-ENG"]))` were English natives tested in Catalan, and `r length(unique(participants$participant_id[participants$group=="cat-SPA"]))` were Spanish natives tested in Catalan. `r sum(!participants$valid_participant)` failed to meet all the inclusion criteria and were excluded from further analyses. The final sample comprised data from `r sum(!participants$valid_participant)` participants, `r sum(participants$valid_participant[participants$group=="spa-ENG"])` in the spa-ENG group, `r sum(participants$valid_participant[participants$group=="cat-ENG"])` in the cat-ENG group, and `r sum(participants$valid_participant[participants$group=="cat-SPA"])` in the cat-SPA group.

@@

participants_coded %>% 
  count(
    group, 
    valid_participant
  ) %>% 
  mutate(valid_participant = factor(valid_participant)) %>% 
  ggplot() +
  aes(
    group,
    n, 
    fill = valid_participant,
    order = n
  ) + 
  geom_col() +
  labs(
    x = "Group", 
    y = "# participants", 
    fill = "Valid?"
  ) +
  theme(
    legend.title = element_blank(),
    legend.position = "top",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(
      linetype = "dotted", 
      colour = "grey"
    )
  )

@@

participants_coded %>% 
  filter(valid_participant=="Valid") %>% 
  select(
    participant_id, 
    group, 
    n,
    n_valid
  ) %>%
  mutate(valid_prop = n_valid/n) %>% 
  ggplot() +
  aes(
    x = valid_prop, 
    fill = group,
    colour = group
  ) + 
  facet_wrap(~group, ncol = 1) +
  geom_histogram() +
  geom_rug() +
  labs(
    x = "Valid trials (%)",
    y = "N participants",
    fill = "Group",
    colour = "Group"
  ) +
  scale_x_continuous(labels = percent) +
  theme(
    legend.title = element_blank(),
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(
      linetype = "dotted", 
      colour = "grey"
    )
  )
```

@@

```{r participants_demo, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants_valid <- filter(
  participants_coded,
  valid_participant=="Valid"
)

p_sex <- participants_valid %>% 
  left_join(count(participants_valid, group, name = "n_total")) %>% 
  mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
  ggplot() +
  aes(
    x = group, 
    fill = sex
  ) +
  geom_bar(position = position_fill()) +
  labs(
    x = "Group", 
    y = "# participants", 
    fill = "Sex"
  ) +
  scale_y_continuous(labels = percent) +
  theme(
    legend.position = "top",
    axis.title.x = element_blank()
  )

p_age <- participants_valid %>% 
  left_join(count(participants_valid, group, name = "n_total")) %>% 
  mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
  ggplot(
    aes(
      as.factor(age),
      fill = group,
      colour = group
    )
  ) +
  facet_wrap(~group, ncol = 1) +
  geom_bar(colour = "white") +
  labs(
    x = "Age (years)", 
    y = "% participants", 
    fill = "Group", 
    colour = "Group"
  ) +
  theme(
    legend.position = "none"
  )

(p_sex + p_age) &
  plot_layout() &
  plot_annotation(tag_levels = "A") &
  theme(
    legend.title = element_blank(),
    panel.grid.major.y = element_line(
      linetype = "dotted", 
      colour = "grey"
    )
  )

@@

participants_valid %>% 
  count(group, l2, .drop = FALSE) %>% 
  mutate(
    l2 = case_when(
      l2=="Alemã\u0081n" ~ "German",
      l2=="Francã\u2030s" ~ "French",
      l2=="Cuã\u0081l" ~ "Missing",
      TRUE ~ l2
    ),
  ) %>% 
  left_join(
    count(
      participants_valid, 
      group, 
      name = "n_total"
      )
    ) %>% 
  mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
  ggplot() +
  aes(
    group,
    n,
    fill = l2
  ) + 
  facet_wrap(
    ~group, 
    ncol = 1,
    scales = "free_y"
  ) +
  geom_col(position = position_fill()) +
  labs(
    x = "L2", 
    y = "# participants", 
    fill = "L2"
  ) +
  scale_y_continuous(labels = percent) +
  coord_flip() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    strip.text = element_blank(),
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 90),
    axis.title.y = element_blank()
  )

@@

participants_valid %>% 
  select(
    participant_id, 
    group,
    catalan_oral, 
    spanish_oral, 
    catalan_written,
    spanish_written
  ) %>% 
  mutate_at(
    vars(
      catalan_oral,
      spanish_oral,
      catalan_written,
      spanish_written
    ), 
    replace_na, 
    0
  ) %>% 
  pivot_longer(
    c(
      catalan_oral,
      spanish_oral, 
      catalan_written, 
      spanish_written
    ),
    names_to = "type",
    values_to = "score"
  ) %>% 
  separate(
    type, 
    c("language", "modality"), 
    sep = "_"
  ) %>% 
  mutate_at(
    vars(language, modality), 
    str_to_sentence
  ) %>%
  left_join(
    count(
      participants_valid,
      group, 
      name = "n_total"
      )
    ) %>% 
  mutate(group = paste0(group, " (N = ", n_total, ")")) %>% 
  ggplot(
    aes(
      as.integer(score), 
      fill = language)
  ) +
  facet_grid(modality~group) +
  geom_bar(
    position = position_dodge(),
    colour = "white"
  ) +
  labs(
    y = "# participants", 
    x = "Self-reported proficiency (0-5)",
    fill = "Language"
  ) +
  theme(
    legend.position = "top",
    panel.grid.major.y = element_line(
      colour = "grey",
      linetype = "dotted"
    )
  )

@@

```{r responses_coded, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
responses_coded <- responses %>% 
  # typos are considered correct responses
  mutate_at(vars(group), as.factor) %>% 
  # center predictors
  mutate_at(
    vars(lv_std, pthn_std, frequency_zipf_std),
    function(x) scale(x, center = TRUE, scale = TRUE)[,1]) %>% 
  # impute missing data
  as_tibble() %>% 
  arrange(group, word)
```

@@

coefs <- fixef(fit_6) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(
    vars(estimate:q97_5), 
    ~ifelse(
      variable=="Intercept",
      inv_logit_scaled(.),
      ./4
    )
  )

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:groupeng_spa" = "Levenshtein \u00d7 Group 1",
  "lv_std:groupcateng_spaeng" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "groupeng_spa" =  "Group 1\n[ENG-* vs. cat-SPA]",
  "groupcateng_spaeng" = "Group 2\n[cat-ENG vs. spa-ENG]"
)

coefs %>% 
  mutate(
    variable = str_remove(variable, "b_") %>% 
      str_replace_all(str_repl) %>%  
      factor(
        levels = c(
          "Intercept", "Frequency\n[+1 SD]", "PTHN\n[+1 SD]", 
          "Levenshtein\n[+1 SD]", "PTHN \u00d7 Levenshtein",
          "Group 1\n[ENG-* vs. cat-SPA]",
          "Group 2\n[cat-ENG vs. spa-ENG]",
          "Levenshtein \u00d7 Group 1", "Levenshtein \u00d7 Group 2"
        )
      )
  ) %>% 
  select(-est_error) %>% 
  gt() %>% 
  fmt_percent(2:4) %>% 
  cols_merge(
    c("q2_5", "q97_5"), 
    pattern = "[{1}, {2}]"
  ) %>% 
  cols_label(
    variable = md("**Predictor**"),
    estimate = md("**Mean**"),
    q2_5 = md("**95\\% CrI**"),
  ) %>% 
  tab_source_note("Estimated posterior distributions of coefficients in Model 6. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution.") %>% 
  cols_align(align = "left") %>% 
  as_raw_html()
```
